---
title: "Characterization of individual RNA classes"
knit: (function(input_file, encoding) {
  out_dir <- '.';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
---

```{r setup, include=FALSE, echo = F}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plotly)
library(shiny)
library(data.table)
```

```{r expressionRNAclasses, echo = F}
data <- fread("https://raw.githubusercontent.com/utnesp/Neuroblastoma_Biomarker_2018/master/docs/CPM.cumulative.freq.txt")

shapes = c(15, 16, 17, 0, 18, 3, 5, 2, 8, 24, 1, 25, 4, 7, 8, 9, 10, 26:30)
s <- data.frame(gene_biotype = data$gene_biotype[!duplicated(data$gene_biotype)], shape = shapes[1:length(unique(data$col))] , color = unique(data$col))
p1 <- suppressWarnings(ggplot(data, aes(CPM, CumulativeFrequency)) + geom_point(aes(shape = gene_biotype, color = gene_biotype, 
 text = paste("GENE: ", paste(external_gene_name, "(", ensembl_gene_id, ")", sep = ""), "\nGENE LENGTH (bp):", GeneLength)), size = 1) + theme_classic() + labs(x = "Average expression across cell lines (log2 CPM)", y = "Cumulative Relative Frequency", color='Biotype') + theme(legend.position = "right") + 
       scale_colour_manual(name = "Biotype",
                            labels = s$gene_biotype,
                            values = as.character(s$color))  +
        scale_shape_manual(name = "Biotype",
                           labels = s$gene_biotype,
                           values = s$shape) +
        theme(text = element_text(size = 10), axis.text = element_text(size = 10)))
suppressMessages(ggplotly(p1 + theme(text = element_text(size = 10), axis.text = element_text(size = 10), legend.text = element_text(size = 10)), width = 1000, height = 1000))

```
Supplementary figure to "Clinically relevant biomarker discovery in high-risk recurrent neuroblastoma". 

Each point in the plot corresponds to an individual gene. X- and Y-axis represent the average CPM across all cell lines (log2 transformed) and the cumulative relative frequency, respectively. Numbers in parenthesis correspond to number of genes within each RNA class. A mouse over will show gene biotype, gene name, ENSEMBL gene id, gene length in base pairs, mean CPM across samples and the cumulative relative frequency. Related to Figure 2.
CPM Counts Per Million, lincRNA long intergenic RNAs

